The Privacy of Private Browsing

### 2013-12-15 finalproject/paper.tex
finished browser problems

  \section{Applications: Forensics}
  One of the biggest problems with private browsing sessions is that artifacts
  remain on a machine after the user exits his or her internet browser. These
  artifacts can include logon information for websites, browsing history,
  and digital media such as images and videos---all items that you would expect
  a private browsing session to keep private.\cite{ohana13}

  This section will first summarize locations on a Windows machine where
  private browsing artifacts might be found. An overview of what specific
  artifacts were found for each browser using different forensic techniques
  will follow. The use of SQLite to investigate specific browser artifacts will
  then be discussed.

@@

    \subsection{Firefox}
	In 2011, researchers discovered that Firefox 3.6.11 stored browser history
	and search engine keywords in the computer's physical memory and that this
	information could be accessed after the browsing session was terminated.
	An analysis of the contents of pagefile.sys revealed similar information.
	\cite{said11} Additionally, digital certificates received during private 
	browsing sessions in Firefox 3.6 were not removed from their on-disk 
	database once the browsing session was terminated.\cite{aggarwal10}

    \subsection{Google Chrome}
    One 2013 study stated that it was more difficult to retrieve private
	browsing artifacts from Chrome's incognito mode than Firefox or Internet
	Explorer.\cite{said11}

    \subsection{Internet Explorer}
    Internet Explorer leaves the most artifacts behind when its InPrivate
    Browsing mode terminates.\cite{ohana13} Internet Explorer 8.0.6001.18702
	continued to cache web pages on the hard drive during an InPrivate
	Browsing session, but these files were deleted once the browser window was
	closed. This means that fragments of these files---and thus a record of the
	user's browsing history---could be discovered by analyzing the free and
	slack space of the hard drive.\cite{said11}

>>>>

  \section{Applications: Forensics}
  One of the biggest problems with private browsing sessions is that artifacts
  remain on a machine after the user exits his or her internet browser. These
  artifacts can include logon information for websites, browsing history,
  and digital media such as images and videos---all items that you would expect
  a private browsing session to keep private.\cite{ohana13} Private browsing
  sessions can be exploited by browser extensions and remote attacks, but this 
  section will focus on artifacts left on a local machine by the browsers 
  themselves.

@@

    \subsection{Firefox}
    In 2011, researchers discovered that Firefox 3.6.11 stored browser history
    and search engine keywords in the computer's physical memory and that this
    information could be accessed after the browsing session was terminated.
    An analysis of the contents of pagefile.sys revealed similar information.
    \cite{said11} The presence of these in-memory artifacts persisted through 
    Firefox 17.0.1.\cite{ohana13} Additionally, digital certificates received 
    during private browsing sessions in Firefox 3.6 were not removed from their 
    on-disk database once the browsing session was terminated.\cite{aggarwal10}

    Researchers demonstrated in 2013 that on-disk files used by Firefox 17.0.1 
    showed modified timestamps after a private browsing session. Even though
    information about the user's activities may not be directly accessible,
    evidence that a private browsing session took place can help forensic
    investigators determine why browsing history cannot easily be located on a
    suspect's machine, especially when analysis of the computer's memory is not
    possible.\cite{ohana13} Firefox 19.0 fixed this problem.\cite{satvat13}

    \subsection{Google Chrome}
    One 2011 study stated that it was more difficult to retrieve private
    browsing artifacts from Chrome's incognito mode (using Chrome 7.0.517.41) 
    than Firefox or Internet Explorer. That study found that, as in Firefox 
    3.6.11, browsing history and search engine keywords could be accessed in 
    the computer's memory after the incognito session terminated. However, it 
    found no on-disk artifacts. Only physical memory contained these artifacts, 
    as the pagefile revealed no traces of the websites visited or searches 
    performed using incognito mode.\cite{said11}

    Chrome 23.0.1271.95, on the other hand, modified timestamps for many files
    when terminating incognito sessions. As with Chrome 7.0.517.41, artifacts 
    related to the user's browsing activities were limited to the computer's 
    memory. However, the pagefile did reveal evidence of a file downloaded
    during an incognito browsing session.\cite{ohana13} The timestamp artifacts
    were still present as of version 25.0.1364.97.\cite{satvat13}

    \subsection{Internet Explorer}
    Internet Explorer leaves the most artifacts behind when its InPrivate
    Browsing mode terminates.\cite{ohana13} Internet Explorer 8.0.6001.18702
    continued to cache web pages on the hard drive during an InPrivate
    Browsing session, but these files were deleted once the browser window was
    closed. This means that fragments of these files---and thus a record of the
    user's browsing history---could be discovered by analyzing the free and
    slack space of the hard drive.\cite{said11} Login information for email
    accounts and full image artifacts were discovered on the machine after an 
    InPrivate Browsing session using Internet Explorer 8.0 as recently as 2013.
    \cite{ohana13} Researchers recently determined that Internet Explorer log 
    files no longer contained evidence of browsing history as of version 
    10.0.9200.16521. This had been an issue in previous versions of the 
    browser.\cite{satvat13}
